THE FUNDAMENTAL CONNECTIONS BETWEEN CLASSICAL HAMILTONIAN MECHANICS, QUANTUM MECHANICS \\ AND INFORMATION ENTROPY

### 2019-12-26 Proceedings/2019-Quantum2019/CarcassiQuantum2019Proceedings.tex
Responding to reviewer's comments

To summarize the arguments laid out in \cite{Carc1}, since the state of the system does not capture the state of the parts, we can imagine these continuously permutating without affecting the dynamics of the whole. The internal motion is then characterized by random variables, which still need to allow for the definition of an invariant density, and therefore they must, for a degree of freedom, form a pair $(U,V)$. As the value of the variable is completely unknown, the distribution will be uniform. We can fix the density $\rho=1$ to be unitary and the standard deviations $\sigma_U=\sigma_V$ to be equal as this internal relabelling cannot affect the state of the system as a whole. The transformations that will affect the system as a whole are the changes in variance and correlation as these would change the value of the integral $\int \rho dudv \propto \sigma_U\sigma_V = \sigma_U^2$. These are the transformations of the type:
\begin{equation}
	\begin{aligned}
	\hat{U} = a U + b V \\
	\hat{V} = -b U + a V
	\end{aligned}
\end{equation}
A complex number $c=a + \imath b$ can be used to identify such transformations. The norm represents the strength of the internal random process, which is proportional to the size of the system, and the phase relates to the correlation as the arccosine of the Pearson coefficient.

We want to stress, again, that we consider the classical state to be a matter distribution $\rho(q^i, k_i)$. Therefore, when comparing classical and quantum mechanics, we should be comparing the properties of our wave function $\psi(q^i)$ to the matter distribution $\rho(q^i, k_i)$, not to points of phase space. A point-particle is the limit where the extent of the distribution can be considered small, and therefore the center of mass is enough for our description. This limit can be performed within both classical and quantum mechanics if the scale of the problem allows, and, because of Ehrenfest's theorem, the behavior is the same. In light of the assumptions, it should be obvious this should be the case: the difference between classical and quantum is in the description of the parts; if the length scales are much greater than those of the system, then it doesn't matter what we assume about the parts.

>>>>

To summarize the arguments laid out in \cite{Carc1}, since the state of the system does not capture the state of the parts, we can imagine these continuously permutating without affecting the dynamics of the whole. The internal motion is then characterized by random variables, which still need to allow for the definition of an invariant density, and therefore they must, for a degree of freedom, form a pair $(U,V)$. As the value of the variable is completely unknown\footnote{One may be tempted to distinguish between the following cases: the internal dynamics is unknown, the internal dynamics is unknowable, the internal dynamics is absent/not defined. In fact, different interpretations of quantum mechanics may take different positions. However, one has to be clear how those cases are going to differ experimentally, or this distinction remains within the philosophical realm. In our case, we are limiting ourselves to posit that the processes we are studying are not sensitive to a further description of the system, which makes a possible internal dynamics automatically unknown. It could be that we will find new processes in the future, it could be that such processes are forever outside of what we can control experimentally or it could be that they do not even exist. We cannot know which case we are in: all we is that know we are not sensitive. As we do not have a way to tell, these cases are not distinguishable to us experimentally and they can be treated as the same case.}, the distribution will be uniform.\footnote{The addition of extra degrees of freedom that do not alter the problem but make it easier to study is something common in math and physics. It is common in probability theory, where adding random variables is a standard technique in proofs. It is common in analysis when extending a real integral to the complex plane. It is common in statistical mechanics in order to study system/environment interactions. It is common in quantum mechanics with purification. In all these cases, we are extending our space while making sure that the result does not depend on the particulars of how it was extended. Adding an internal dynamics to which we are insensitive is just another instance.} We can fix the density $\rho=1$ to be unitary and the standard deviations $\sigma_U=\sigma_V$ to be equal as this internal relabelling cannot affect the state of the system as a whole. The transformations that will affect the system as a whole are the changes in variance and correlation as these would change the value of the integral $\int \rho dudv \propto \sigma_U\sigma_V = \sigma_U^2$. These are the transformations of the type:
\begin{equation}
	\begin{aligned}
	\hat{U} = a U + b V \\
	\hat{V} = -b U + a V
	\end{aligned}
\end{equation}
A complex number $c=a + \imath b$ can be used to identify such transformations. The norm represents the strength of the internal random process, which is proportional to the size of the system, and the phase relates to the correlation as the arccosine of the Pearson coefficient.

We want to stress, again, that we consider the classical state to be a matter distribution $\rho(q^i, k_i)$. Therefore, when comparing classical and quantum mechanics, we should be comparing the properties of our wave function $\psi(q^i)$ to the matter distribution $\rho(q^i, k_i)$, not to points of phase space. Comparing the two mechanics, in fact, means comparing how the same system would be different under the different assumptions. So we have to compare finite systems to finite systems. In both cases, the ``particle'' is the smallest part of the system to which we can assign a state. Yet, in quantum mechanics it is itself the indivisible system, while a classical particle is not a system: it is the limit of recursive subdivision.  While this different comparison may at first seem awkward, as it is not the usual framing, it leads to a more stringent parallel between the mathematical elements of classical and quantum mechanics and, in turn, to a better intuition.

For example, it makes it clear that the position of classical objects (e.g. planets, cannonballs, drops of water and even ourselves) cannot be fully described by a single number, as it is often said. All these objects have extent both in space and momentum. A point-particle is the limit where the extent of the distribution can be considered small, and therefore the center of mass is enough for our description. This limit can be performed within both classical and quantum mechanics if the scale of the problem allows, and, because of Ehrenfest's theorem, the behavior is the same. In light of the assumptions, it should be obvious this should be the case: the difference between classical and quantum is in the description of the parts; if the length scales of interest are much greater than those of the system, then it does not matter what we assume about the parts.
